Modelling and Analysis of an Interventional X-Ray System with NuSMV2

### 2013-07-04 paper/main.tex
final version

		\item \textbf{The system is not prepared or a dose is started if there is an error for the corresponding type and Xplane.} %TODO KLOPT NOG NIET?
			\begin{align*}
				\LTLG &(!\textrm{o.prepared} \land \errorhigh \land (\LTLF !\errorhigh) \\
				&\hspace{1em}	\imply (!\textrm{o.prepared} \LTLU !\errorhigh)) \land \\
				& (\doseno \land \textrm{i.signal = LowFrontOn} \land \textrm{e.FrontLowError} \land (\LTLF !\textrm{e.FrontLowError}) \\
				&\hspace{1em}	\imply (!(\textrm{o.direction = Front} \land \doselow) \LTLU !\textrm{e.FrontLowError})) \land \\
				& (\doseno \land \textrm{i.signal = LowSideOn} \land \textrm{e.SideLowError} \land (\LTLF !\textrm{e.SideLowError}) \\
				&\hspace{1em}	\imply (!(\textrm{o.direction = Side} \land \doselow) \LTLU !\textrm{e.SideLowError})) \land \\
				& (\doseno \land \textrm{i.signal = LowBothOn} \land \errorlow \land (\LTLF !\errorlow) \\
				&\hspace{1em}	\imply (!(\textrm{o.direction = Both} \land \doselow) \LTLU !\errorlow)) \land \\
				& (\textrm{i.signal = StartSeqHigh} \land \textrm{next\_direction = Front} \land \textrm{e.FrontHighError} \land (\LTLF !\textrm{e.FrontHighError}) \\
				&\hspace{1em}	\imply (!(\dosehighseq \land \textrm{o.direction = Front}) \LTLU !\textrm{e.FrontHighError})) \land \\
				& (\textrm{i.signal = StartSeqHigh} \land \textrm{next\_direction = Side} \land \textrm{e.SideHighError} \land (\LTLF !\textrm{e.SideHighError}) \\
				&\hspace{1em}	\imply (!(\dosehighseq \land \textrm{o.direction = Side}) \LTLU !\textrm{e.SideHighError})) \land \\
				& (\textrm{i.signal = StartSeqHigh} \land \textrm{next\_direction = Both} \land \errorhigh \land (\LTLF !\errorhigh) \\
				&\hspace{1em}	\imply (!(\dosehighseq \land \textrm{o.direction = Both}) \LTLU !\errorhigh)) \land \\
				& (\textrm{i.signal = StartOneHigh} \land \textrm{next\_direction = Front} \land \textrm{e.FrontHighError} \land (\LTLF !\textrm{e.FrontHighError}) \\
				&\hspace{1em}	\imply (!(\dosehighone \land \textrm{o.direction = Front}) \LTLU !\textrm{e.FrontHighError})) \land \\
				& (\textrm{i.signal = StartOneHigh} \land \textrm{next\_direction = Side} \land \textrm{e.SideHighError} \land (\LTLF !\textrm{e.SideHighError}) \\
				&\hspace{1em}	\imply (!(\dosehighone \land \textrm{o.direction = Side}) \LTLU !\textrm{e.SideHighError})) \land \\
				& (\textrm{i.signal = StartOneHigh} \land \textrm{next\_direction = Both} \land \errorhigh \land (\LTLF !\errorhigh) \\
				&\hspace{1em}	\imply (!(\dosehighone \land \textrm{o.direction = Both}) \LTLU !\errorhigh))
			\end{align*}
		\item \textbf{For Low dose a degraded mode is used in case of an error, that is, if Xplane Both is requested then}
			\begin{enumerate}
				\item only Xplane Front is used if SideLowError holds;
					\begin{align*}
						(\LTLG !\errorhigh) \imply \LTLG &(\doseno \land \textrm{instr = LowBothOn} \land \textrm{e.FrontLowError} \land (!\LTLF \textrm{e.FrontLowError}) \\
						&\hspace{1em}	\imply \LTLF \textrm{o.direction = Side})
					\end{align*}
				\item only Xplane Side is used if FrontLowError holds.
					\begin{align*}
						(\LTLG !\errorhigh) \imply \LTLG &(\doseno \land \textrm{instr = LowBothOn} \land \textrm{e.SideLowError} \land (!\LTLF \textrm{e.SideLowError}) \\
						&\hspace{1em}	\imply \LTLF \textrm{o.direction = Front})
					\end{align*}
			\end{enumerate}

>>>>

		\item \textbf{The system is not prepared or a dose is started if there is an error for the corresponding type and Xplane.}
			\begin{align*}
				\LTLG &(!\textrm{o.prepared} \land \errorhigh \land (\LTLF !\errorhigh) \\
				&\hspace{1em}	\imply (!\textrm{o.prepared} \LTLU !\errorhigh)) \land \\
				& (\doseno \land \textrm{i.signal = LowFrontOn} \land \textrm{e.FrontLowError} \land (\LTLF !\textrm{e.FrontLowError}) \\
				&\hspace{1em}	\imply (!(\textrm{o.direction = Front} \land \doselow) \LTLU !\textrm{e.FrontLowError})) \land \\
				& (\doseno \land \textrm{i.signal = LowSideOn} \land \textrm{e.SideLowError} \land (\LTLF !\textrm{e.SideLowError}) \\
				&\hspace{1em}	\imply (!(\textrm{o.direction = Side} \land \doselow) \LTLU !\textrm{e.SideLowError})) \land \\
				& (\doseno \land \textrm{i.signal = LowBothOn} \land \errorlow \land (\LTLF !\errorlow) \\
				&\hspace{1em}	\imply (!(\textrm{o.direction = Both} \land \doselow) \LTLU !\errorlow)) \land \\
				& (!\dosehigh \land \textrm{i.signal = StartSeqHigh} \land \textrm{next\_direction = Front} \land \textrm{e.FrontHighError} \\
				&\hspace{1em}	\land (\LTLF !\textrm{e.FrontHighError}) \imply (!(\dosehighseq \land \textrm{o.direction = Front}) \LTLU !\textrm{e.FrontHighError})) \land \\
				& (!\dosehigh \land \textrm{i.signal = StartSeqHigh} \land \textrm{next\_direction = Side} \land \textrm{e.SideHighError}\\
				&\hspace{1em}	\land (\LTLF !\textrm{e.SideHighError}) \imply (!(\dosehighseq \land \textrm{o.direction = Side}) \LTLU !\textrm{e.SideHighError})) \land \\
				& (!\dosehigh \land \textrm{i.signal = StartSeqHigh} \land \textrm{next\_direction = Both} \land \errorhigh \\
				&\hspace{1em}	\land (\LTLF !\errorhigh) \imply (!(\dosehighseq \land \textrm{o.direction = Both}) \LTLU !\errorhigh)) \land \\
				& (!\dosehigh \land \textrm{i.signal = StartOneHigh} \land \textrm{next\_direction = Front} \land \textrm{e.FrontHighError} \\
				&\hspace{1em}	\land (\LTLF !\textrm{e.FrontHighError}) \imply (!(\dosehighone \land \textrm{o.direction = Front}) \LTLU !\textrm{e.FrontHighError})) \land \\
				& (!\dosehigh \land \textrm{i.signal = StartOneHigh} \land \textrm{next\_direction = Side} \land \textrm{e.SideHighError} \\
				&\hspace{1em}	\land (\LTLF !\textrm{e.SideHighError}) \imply (!(\dosehighone \land \textrm{o.direction = Side}) \LTLU !\textrm{e.SideHighError})) \land \\
				& (!\dosehigh \land \textrm{i.signal = StartOneHigh} \land \textrm{next\_direction = Both} \land \errorhigh \\
				&\hspace{1em}	\land (\LTLF !\errorhigh) \imply (!(\dosehighone \land \textrm{o.direction = Both}) \LTLU !\errorhigh))
			\end{align*}
		\item \textbf{For Low dose a degraded mode is used in case of an error, that is, if Xplane Both is requested then}
			\begin{enumerate}
				\item only Xplane Front is used if SideLowError holds;
					\begin{align*}
						(\LTLG !\errorhigh) \imply \LTLG &(\doseno \land \textrm{instr = LowBothOn} \land \textrm{e.FrontLowError} \land (!\LTLF \textrm{e.FrontLowError}) \\
						&\hspace{1em}	\imply \LTLF \textrm{o.direction = Side})
					\end{align*}
				\item only Xplane Side is used if FrontLowError holds.
					\begin{align*}
						(\LTLG !\errorhigh) \imply \LTLG &(\doseno \land \textrm{instr = LowBothOn} \land \textrm{e.SideLowError} \land (!\LTLF \textrm{e.SideLowError}) \\
						&\hspace{1em}	\imply \LTLF \textrm{o.direction = Front})
					\end{align*}
			\end{enumerate}
